\section{Introduction}\label{index_intro_sec}
\subsection*{$\ast$$\ast$\-Welcome to the 0\-Features-\/0\-Bugs\-C\-V\-A3 wiki!$\ast$$\ast$}

For our project, we created an Open\-G\-L Shading Language(glsl) Interactive Development Environment(\-I\-D\-E). The user can load shaders such as 'toon', 'basic metal', 'Phong' and more, then visualise and edit the vertex and fragment shader data using the I\-D\-E. Below are some screenshots\-:  {\itshape Teapot with a texture applied.}  {\itshape Pre-\/defined shape, 'dragon', with high material shininess set.}  {\itshape You can import any triangulated .obj mesh to visualise the shader on.}\section{Authors}\label{index_author_sec}
\begin{TabularC}{2}
\hline
\rowcolor{lightgray}{\bf Name }&{\bf Git\-Hub Account  }\\\cline{1-2}
Jonathan Lyddon-\/\-Towl &jlyddon \\\cline{1-2}
Adam Ting &yadang23 \\\cline{1-2}
Jonathan Flynn &J\-F\-Designer \\\cline{1-2}
Ellie Ansell &Ellie\-Ansell \\\cline{1-2}
Philip Rouse &philrouse \\\cline{1-2}
Anand Hotwani &anandhotwani \\\cline{1-2}
Alexander La Tourelle &main\-Confetti \\\cline{1-2}
\end{TabularC}
\section{How to use}\label{index_howto_sec}
{\bfseries H\-O\-W T\-O U\-S\-E C\-E\-B\-:} {\bfseries Navigating the viewport.} The viewport manipulation is similar to most 3\-D software packages. Using the left mouse button you can rotate the viewport; moving the right mouse button allows you to pan and you can zoom in and out by scrolling the mouse wheel. If you accidentally lose focus of the object, hit 'F' or click 'reset' in camera settings to revert to the default view. In the 'settings' tab, camera controls include roll, yaw, pitch, a slider to set the F\-O\-V and the option to change the clipping plane distance. The camera's orthographic view can be set and reset, too. Below the camera settings are visibility switches which can be toggled to show the axis, grid, wireframe ('w') and normals ('n'), and the slider will adjust their size. Below these are the options to export and print uniforms to be saved.

 {\itshape The default view window.}

1) {\bfseries Writing your first shader} Upon opening the project, you can either choose to load fragment and vertex shaders via the shader wizard window or simply press 'Esc' to skip to playing with C\-E\-B. The default shader in C\-E\-B is a normal material which softly reflects light. To begin, load the preset shaders included in the project for both the vertex and fragment shaders\-: {\bfseries File-\/$>$ Import Shaders -\/$>$ Import Vertex Shader / Import Fragment Shader} (Or Ctrl+\-Shift+v / Ctrl+\-Shift+v)

The library includes plastic, metal and toon shading as well as a shader with texture mapping support. Compiling any of these shaders will prompt the Uniform buttons to appear. From here you can affect parameters such as ambient, colour, light position to visualise the shader applied.

 {\itshape The default window and with normal material.}

Use the central buttons (colour, light.\-ambient, light.\-constant\-Attenuation etc.) to change how the object looks. You can edit the shader files directly via the vertex and fragment text editors, then clicking 'compile shader' to see the results. Auto-\/correct is incorporated into the editor, as well as syntax highlighting. Errors are thrown to the error log in the compiler.  {\itshape Default shape dragon with high material shininess and a metal shader.}

2) {\bfseries Loading in custom .O\-B\-J files} C\-E\-B already contains a selection of .obj files and primitive shapes to start, but you can also load in your own files provided they're triangulated beforehand. {\bfseries Load Shapes -\/$>$ Import O\-B\-J}

 {\itshape Importing a custom obj file}

3) {\bfseries Applying texture maps} To load texture maps, first import the Texture\-Map\-Vertex and Texture\-Map\-Fragment shaders. Then go\-: {\bfseries Load Texture -\/$>$ Load Texture...} \-\_\-(Ctrl + T)\-\_\- Loading in custom texture maps for diffuse values are supported in C\-E\-B. Some example texture maps are included in the project, however you are free to use custom maps. Note\-: the shader needs to support texture maps to work.

 {\itshape Texture map example.}

4) {\bfseries Loading in custom .glsl files} C\-E\-B also supports loading in custom G\-L\-S\-L files directly in the I\-D\-E. (Note that this will overwrite any text currently in the editor.) Using this you can load in any presets provided or your own. By going File$>$Import Shaders you can choose either Fragment or Vertex. 

5) {\bfseries Saving and loading files} C\-E\-B supports saving and loading the shader project files in .xml format. Saving and loading are both accessed via the \char`\"{}\-File\char`\"{} tab\-: {\bfseries File -\/$>$ save project as...} \-\_\-(Ctrl+\-Shift+s)\-\_\-

{\bfseries File -\/$>$ Open project...} \-\_\-(Ctrl+\-O)\-\_\-

 {\itshape Loading a saved project file.}

6) {\bfseries Using the \doxyref{Project}{p.}{class_project} Wizard} Using the \doxyref{Project}{p.}{class_project} Wizard is designed to help the user to create shaders. By setting a new project the user can specify their desired version of G\-L\-S\-L, profile, project name as well as associated vertex and fragment shaders.  {\itshape The project wizard upon opening}  {\itshape Choosing the name of your project}  {\itshape Loading the phong vertex/ fragment shaders}

7) {\bfseries Exporting Shader Uniforms} If you find particular uniform set-\/ups that work well and you would like to re-\/use in other projects or shaders, you have the ability to export them for later use. These are saved out as text files and can also be run in the Terminal to confirm the exporting.  {\itshape Exporting the uniforms}  {\itshape Exported the uniforms successfully.}

The pop-\/up reads \char`\"{}\-Uniform data successfully exported!\char`\"{}, and a text editor shows the written data saved as a .txt file to be used in other applications.  